---
title: "final project subscript"
author: "Lizhao"
date: '2022-05-06'
output: html_document
---
### create the independent variable matrix, include all abilities indexes


```{r pressure, echo=FALSE}
ability_indexes <- Analyzed_data %>% 
  na_if("")%>% select("Crossing","Finishing","HeadingAccuracy",
                             "ShortPassing","Volleys","Dribbling","Curve",
                             "FKAccuracy","LongPassing","BallControl",
                             "Acceleration","SprintSpeed","Agility",
                             "Reactions","Balance","ShotPower","Jumping",
                             "Stamina","Strength","LongShots","Aggression",
                             "Interceptions","Positioning","Vision",
                             "Penalties","Composure","Marking",
                             "StandingTackle","SlidingTackle","GKDiving",
                             "GKHandling","GKKicking","GKPositioning",
                             "GKReflexes")


ability_indexes <- na.omit(ability_indexes)

ability_indexes_scale = scale(ability_indexes, center=TRUE, scale=TRUE)

mu = attr(ability_indexes,"scaled:center")
sigma = attr(ability_indexes,"scaled:scale")


```

### can cluster model help us distinguish sth? Wage? Age? position?

ATTENTION: cluster model use ability_index, don't include age, wage,or other thing,

```{r cluster based on their abilities, echo=FALSE}
set.seed(10000)
clust1 = kmeans(ability_indexes_scale, 5, nstart=25)
clust1$size
clust1_sum <- clust1$center%>% as.data.frame()%>%rownames_to_column('cluster_No')
clust1_sum
v = clust1$cluster
```

```{r show each cluster wage and age, echo=FALSE}
Analyzed_data <- Analyzed_data %>% mutate(clust_No = v)
ggplot(data = Analyzed_data)+ geom_point(aes(x = wage_amount, y = Age,  ), alpha = 0.2, ) + coord_flip()+
  facet_wrap(~clust_No)


ggplot(data = Analyzed_data)+ geom_histogram(aes(x = Potential,  ), alpha = 0.2, ) + 
  facet_wrap(~clust_No)

```


#### can I describe my finding according to these plots?

```{r plot any other variables based on cluster number, echo=FALSE} 
ggplot(data = Analyzed_data)+ geom_point(aes(x = wage_amount, y = Age, color = factor(clust_No) ), alpha = 1, )

```

Also, we can test weight, height
```{r weight and height, echo=FALSE}
#https://stackoverflow.com/questions/47667994/ggplot-x-axis-labels-with-all-x-axis-values

ggplot(data = Analyzed_data)+ geom_point(aes(x = weight_amount, y = height_cm, color = factor(clust1$cluster)), alpha = 0.2, ) +theme(axis.text.x = element_text(angle=45, vjust=.5, size = 0.6, hjust=1))+scale_x_discrete(breaks = seq(110,250,10))


```



cluster them into 10 clusters, since there are 27 positions

```{r try to disinguish position, include=FALSE}
set.seed(10000)
clust2 = kmeans(ability_indexes_scale, 10, nstart=100)
clust2$size
clust2_sum <- clust2$center%>% as.data.frame()%>%rownames_to_column('cluster_No')
clust2_sum
v_2 = clust2$cluster

```


```{r show the plots for each cluster about their position, echo=FALSE}
Analyzed_data <- Analyzed_data %>% mutate(clust_No_2 = v_2)
ggplot(data = Analyzed_data)+ geom_bar(aes(x = Position, ), alpha = 0.2, ) + theme(axis.text.x = element_text(angle=45, vjust=.5, hjust=1, ))+
  facet_wrap(~clust_No_2)

```

## whether we can predict a player preferred Foot? based on different methods

try to use lasso to calculate whether a palyers preferred foot binomial variable ----- lasso (glmnet does L1-L2, gamlr does L0-L1)

RHS var is perferred foot is left or right?   (binomial variable 0 and 1)
LHS vars are ability indexes
