---
title: "Exercise2"
author: "Jonathan"
date: "3/7/2022"
output: md_document
---
Author:
LiZhao Du
YiJi Gao
Jyun-Yu Cheng


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Question 1
```{r,echo=FALSE, message= FALSE, warning=FALSE}
library(RCurl)
library(tidyverse)
library(mosaic)
library(curl)
library(ggplot2)
capmetro_UT = read.csv('https://raw.githubusercontent.com/jgscott/ECO395M/master/data/capmetro_UT.csv')
```

```{r,echo=FALSE, message= FALSE, warning=FALSE}
#把categorical variables按合理的排列，不按字母順序排
#mutate用來新增資料框（衍生變數or非衍生變數都可以）
capmetro_UT = mutate(capmetro_UT,
                     day_of_week = factor(day_of_week,
                     levels=c("Mon", "Tue", "Wed","Thu", "Fri", "Sat", "Sun")),
                     month = factor(month, levels=c("Sep", "Oct","Nov")))

```

```{r,echo=FALSE, message= FALSE, warning=FALSE}
#calculate the average boarding time by group
#summarize 中輸入摘要對象的資料框(capmetro_UT，以及欲摘要的變數名稱（mean)
#先把campmetro_UT按hour of day, day of week,month去分群(by group_by，再使用summarize去計算mean(by summarize),命名為meanboarding

average_boarding = capmetro_UT %>%
  group_by(hour_of_day, day_of_week, month) %>%
  summarize(mean_boarding = mean(boarding)) 
average_boarding
```

```{r,echo=FALSE, message= FALSE, warning=FALSE}
#add a new variable which is called "week" to separate the weekday and weekend
week = mutate(capmetro_UT, weekdays = day_of_week == "Mon", "Tue", "Wed","Thu", "Fri", weekend = day_of_week == "Sat", "Sun")
```

```{r,echo=FALSE, message= FALSE, warning=FALSE}
#graph 1
#geom_line後面是規定x軸、y軸,color
#facet_wrap是將圖照day_of_week去分類
#scale_color_manual是更改線的顏色
ggplot(average_boarding) +
  geom_line(aes(x = hour_of_day, y=mean_boarding, color=month)) +
  facet_wrap(~day_of_week) +
  labs(title="Average boardings grouped by hour of the day, day of week, and month", y="Mean_boarding", x="Hour of day") +
  scale_color_manual(values = c('blue','red','green')) 

head(capmetro_UT)
```

```{r,echo=FALSE, message= FALSE, warning=FALSE}
# graph2
average_boarding_temperature = capmetro_UT %>%
  group_by(temperature, hour_of_day,  weekend) %>%
  summarize(mean_boarding = mean(boarding)) 
average_boarding_temperature

ggplot(average_boarding_temperature) +
  geom_point(aes(x = temperature, y=mean_boarding, color=weekend)) +
  facet_wrap(~hour_of_day) +
  labs(title="Average boardings grouped by temperature and week", y="Mean boarding", x="Temperature") +
  scale_color_manual(values = c('darkblue','darkgreen'))
```
Problem1:
(1)The hour of peak of boarding is almost the same from day to day, its range is about from 4 p.m. to 5 p.m.

(2)The reason that average boarding on Mondays in September look lower, compared to other days and months, is the summer break just finish, so not all the students come back.

(3)The reason that average boarding on Weds/Thurs/Fri in November look lower is because of the Thanksgiving holiday , which lower the the average boarding of November.

Problem2:
When we hold hour of day and weekend status constant, temperature seems have not an noticeable effect on the number of UT students riding the bus,the line is horizontal.

#Question4

```{r,echo=FALSE, message= FALSE, warning=FALSE}

library(tidyverse)
library(ggplot2)
library(modelr)
library(rsample)
library(mosaic)
library(lubridate)
library(ModelMetrics)



hotels_dev <- read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/hotels_dev.csv")
hotels_val <- read.csv("https://raw.githubusercontent.com/jgscott/ECO395M/master/data/hotels_val.csv")
```
Using only the data in hotels.dev.csv, please compare the out-of-sample performance of the following models:

```{r,echo=FALSE, message= FALSE, warning=FALSE}
hotels_dev = mutate(hotels_dev, Time = ymd(arrival_date), month = month(Time) %>% factor())
hotels_val = mutate(hotels_val, Time = ymd(arrival_date), month = month(Time) %>% factor())

hotels_dev_split = initial_split(hotels_dev, prop = 0.8)
hotels_dev_split_train = training(hotels_dev_split)
hotels_dev_split_test = testing(hotels_dev_split)

# baseline 1: a small model that uses only the market_segment, adults, customer_type, and is_repeated_guest variables as features.
lm1 = lm(children ~ market_segment + adults + customer_type + is_repeated_guest,  data = hotels_dev_split_train,)
lm2 = lm(children ~ . -arrival_date, data = hotels_dev_split_train,)
# transfer arrival_date  as a time stamp,  in a specific format: Y-M-D    feature-engineer.R

lm3 = lm(children ~ . -arrival_date + market_segment:distribution_channel + month, data = hotels_dev_split_train,)

glm1 = glm(children ~ market_segment + adults + customer_type + is_repeated_guest,  data = hotels_dev_split_train, family = 'binomial')
glm2 = glm(children ~ . -arrival_date, data = hotels_dev_split_train, family = 'binomial')
glm3 = glm(children ~ . -arrival_date + market_segment:distribution_channel + month, data = hotels_dev_split_train, family = 'binomial')

rmse(lm1, hotels_dev_split_test)
rmse(lm2, hotels_dev_split_test)
rmse(lm3, hotels_dev_split_test)
rmse(glm1, hotels_dev_split_test)
rmse(glm2, hotels_dev_split_test)
rmse(glm3, hotels_dev_split_test)
```


```{r,echo=FALSE, message= FALSE, warning=FALSE}
#Model validation: step 1
# spamtoy.R

probhat = predict(lm3, newdata = hotels_val)
probs <- exp(probhat)/(1 + exp(probhat))

probhat_2 <- predict(glm3, newdata = hotels_val)



# or get probability directly use
#pred = predict(glm3, newdata = hotels_val, type = 'response')
#head(pred)

#children_hat =  ifelse(probhat >= 0.5, 1, 0)
#table(children = hotels_val$children, children_hat = children_hat)


library(ROCR)

# ROC curve
#https://www.bilibili.com/video/BV1Y64y1Z7Ht
ROCR = prediction(probhat, hotels_val$children)
perf = performance(ROCR, 'tpr','fpr')

ROCR_2 = prediction(probhat_2, hotels_val$children)
perf_2 = performance(ROCR_2, 'tpr', 'fpr')

x <- unlist(perf@x.values)
y <- unlist(perf@y.values)
plotdata <- data.frame(x,y)
names(plotdata) <- c('x', 'y')

g <- ggplot(plotdata)+ 
  geom_path(aes(x = x, y = y, color = x), size =1)+
  labs(x = 'False positive rate', y = 'True positive rate', title = 'ROC Curves based on linear model')
  
x_2 <- unlist(perf_2@x.values)
y_2 <- unlist(perf_2@y.values)
plotdata_2 <- data.frame(x_2,y_2)
names(plotdata_2) <- c('x_2', 'y_2')

g_2  <- ggplot(plotdata_2)+ 
  geom_path(aes(x = x_2, y = y_2, color = x_2), size =1)+
  labs(x = 'False positive rate', y = 'True positive rate', title = 'ROC Curves based on logit model')
```


```{r,echo=FALSE, message= FALSE, warning=FALSE}
hotels_val_split = initial_split(hotels_val, prop = 0.8)
hotels_val_split_train = training(hotels_val_split)
hotels_val_split_test = testing(hotels_val_split)
library(caret)

set.seed(100)
indexs = createFolds(1:dim(hotels_val)[1], k = 20, list = TRUE, returnTrain = FALSE)
err_result = c()
model = glm(children ~ . -arrival_date + market_segment:distribution_channel + month, data = hotels_val, family = 'binomial')
for (i in 1:20){
  slice_data = hotels_val[indexs[[i]],]
  prediction = predict(model,newdata = slice_data,type = "response")
  predict_num = round(mean(prediction)*dim(slice_data)[1])
  ### expected number of bookings with children for that fold.
  actual_num = sum(slice_data$children)
  err_result = rbind(err_result,c(actual_num,predict_num))
} 

# The following is the summary of expected number of bookings with children for that 
# fold and actual number

err_result = data.frame(err_result)
colnames(err_result)=c("actual_num","predict_num") 
err_result$difference = err_result$predict_num-err_result$actual_num
print(err_result)

# The following figure demonstrates the distribution of difference beween actual number
# and expected number.
p0 = ggplot(data=err_result) + 
  geom_histogram(aes(x=difference)) 
p0
```